---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# hydrocan

<!-- badges: start -->
[![R-CMD-check](https://github.com/HakaiInstitute/hydrocan/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/HakaiInstitute/hydrocan/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

> **Warning:** This package is in very early development. The API may change without notice and it should not be used in production.

hydrocan provides unified access to Canadian hydrometric data from diverse
web-published sources. It is complementary to
[tidyhydat](https://docs.ropensci.org/tidyhydat/), which covers the federal
Water Survey of Canada (WSC) network. hydrocan adds provincial and utility
networks that have no existing R package.

Every function returns a consistent tibble regardless of the underlying data
source, so analysis code works unchanged as new sources are added.

## Installation

```{r install, eval = FALSE}
# install.packages("pak")
pak::pak("HakaiInstitute/hydrocan")
```

## Usage

The two main functions are `hc_read_flows()` for sub-daily observations
and `hc_read_daily_flows()` for daily aggregates. Both accept one or more
station numbers, a date range, and an optional `source` argument to target a
specific adapter directly.

```{r usage}
library(hydrocan)

# Sub-daily flow observations - source auto-detected from station number
hc_read_flows(
  station_number = "3-230",
  start_date = Sys.Date() - 7,
  end_date = Sys.Date()
)

hc_read_daily_flows(
  station_number = "3-230",
  start_date = Sys.Date() - 7,
  end_date = Sys.Date()
)
```

## Supported sources

```{r}
hc_list_sources()
```


